Optimal (Multiway) Spatial Joins

### 2024-06-01 5.2.tex

\noindent \underline{\em Proof of Statement (3).}
We will provide a way to map each pair $(\bm{t'}, r)\in \J(R_1,...,R_{k-3},H',V) \times \contained_{R_{k-2}}(\bm{t})$ to a unique tuple in $\J_2$. Consider an arbitrary pair $(\bm{t'}, r)$. Let $h$ be the full segment of $\bm{t'}[k-2]$. We map $(\bm{t'}, r)$ to the tuple $\bm{t} = (\bm{t}'[1],...,\bm{t}'[k-3], r, h, \bm{t}'[k-1])$. By Statement (1) and the fact that $r\in \contained_{R_{k-2}}(\bm{t'})$, the $k$-tuple $\bm{t}$ belongs to $\J_2$.

>>>>

\noindent \underline{\em Proof of Statement (3).}
We will provide a way to map each pair $(\bm{t'}, r)$ satisfyint that $\bm{t'}\in \J(R_1,...,R_{k-3},H',V)$ and $r \in \contained_{R_{k-2}}(\bm{t})$ to a unique tuple in $\J_2$. Consider an arbitrary such pair $(\bm{t'}, r)$. Let $h$ be the full segment of $\bm{t'}[k-2]$. We map $(\bm{t'}, r)$ to the tuple $\bm{t} = (\bm{t}'[1],...,\bm{t}'[k-3], r, h, \bm{t}'[k-1])$. By Statement (1) and the fact that $r\in \contained_{R_{k-2}}(\bm{t'})$, the $k$-tuple $\bm{t}$ belongs to $\J_2$.
